%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/onuratasaritas/}{\Large Onur Ata Sarıtaş}} & Email : \href{mailto:onuratasaritas@gmail.com}{onuratasaritas@gmail.com}\\
  \href{https://github.com/onuratasaritas/}{https://github.com/onuratasaritas} & Mobile : +90-506-341-5399 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Çankaya University}{Ankara, Turkey}
      {Bachelor of Science in Computer Engineering;  GPA: 2.70/4.00}{Sep. 2015 -- Jun. 2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Yemeksepeti}{Istanbul, Turkey}
      {Software Engineer}{Apr 2021 - Present}
\resumeItemListStart
       \resumeItem{Global Joker}
         {Providing REST APIs to DeliveryHero Branches from all over the world by using AWS Lambda Serverless Architecture(API Gateway, RDS, Redis etc.) and .NET Core 2.1}
          \resumeItem{Global Joker Admin Portal}
         {Providing a centralized admin panel which enables entities to manage their specialized configurations, track action logs, reports. Developed on Angular, hosted on S3 using CloudFront which ensures remote regions routes edge locations}
       \resumeItem{Joker Scheduled Tasks}
         {Dockerized several scheduled tasks previously running on \textbf{EC2}. Created \textbf{ECS} architecture and migrated existing code to be run on schedule, using \textbf{FARGATE}}
      

      \resumeItemListEnd
    \resumeSubheading
      {BITES Defence \& Aerospace Technologies}{Ankara, Turkey}
      {Software Engineer}{Oct 2019 - March 2021}
      \resumeItemListStart
       \resumeItem{XperMeet / BizBize}
        {is a reliable, scalable video communications system. Worked on designing and implementing the microservice architecture, using multiple languages and frameworks. Developed a platform-independent system using \textbf{gRPC} and \textbf{.NET Core} 3.1, it was capable of building the data layer independent of platform or framework, using Google's \textbf{Protobuf}. Using Code-First implementations and \textbf{Docker}, the system can cold-start and be scalable from the ground up}
        
       \resumeItem{XperLMS}
         {is a SCORM compliant, highly scalable learning management system. Developed from scratch using gRPC and .NET Core 3.1. Worked as the sole developer. Used in government and military trainings, available on premise or cloud.}
          \resumeItem{Command Center VR}
         {is a virtual presence application designed for military professionals. Developed as a proof-of-concept using \textbf{Oculus SDK} for Oculus Rift S and Oculus Quest, it is a sandbox containing military drills from SWORD by MASAGROUP, for users to connect with a secure connection and have meetings in virtual space, planning and making decisions in a war-room environment. Designed and implemented water, cloud shaders for AndroidVR with a limited processing power.}
       \resumeItem{XperDrive}
         {is a state-of-the-art \textbf{E2EE file manager}. Developed from scratch using gRPC and .NET Core 3.1. Implemented Bouncy Castle for the encryption service. Available as an on-premise solution for the Turkish Government.}
         \resumeItem{XperPay}
         {is a \textbf{payment system} implementing banking services for users: transactions, refunds, recurring payments. Implemented an API for financial technology service Iyzico.}
         \resumeItem{Supplier Decision Support System (TKDS)}
         {is made for \textbf{ASELSAN} to support the banking-finance branch. ASELSAN is the largest defense electronics company in Turkey, and BITES is a subsidiary of ASELSAN and is the branch focusing on for VR/AR/AI solutions. Developed in Django, worked closely with finance branch, delivered time-sensitive features successfully.}

      \resumeItemListEnd
      
      \resumeSubheading
      {Çankaya University}{Ankara, Turkey}
      {Research and Teaching Assistant}{Oct 2017 - May 2018}
      \resumeItemListStart
        \resumeItem{Instructor}
          {Worked 20 hours per week instructing in the following topics practical lectures: 
          
\ \textit{Object Oriented Programming},
         \ \textit{Data Structures},
         \ \textit{Numerical Analysis},
         \ \textit{Data Communications},
         \ \textit{Computer Networks}
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C#, Python, C++, Go, TypeScript}
      \hfill
    }
    \item{
      \textbf{Technologies}{: AWS, Docker, .NET Core, gRPC, PostgreSQL, React/Angular/Vue}     
      \hfill
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
